TrueSkill Through Time: \\ the \proglang{Julia}, \proglang{Python} and \proglang{R} packages

### 2021-07-27 doc/article.tex
Affiliation and keywords

%% - \author{} with primary affiliation
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Gustavo Landfried \\Universidad de Buenos Aires
   \And Esteban Mocskos \\Universidad de Buenos Aires}
\Plainauthor{Gustavo Landfried, Esteban Mocskos }

%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{TrueSkill Through Time: \\ the \proglang{Julia}, \proglang{Python} and \proglang{R} packages}
\Plaintitle{TrueSkill Through Time: the Julia, Python and R packages}
\Shorttitle{TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages (Draft)}

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
  Gustavo Andr\'es Landfried\\
  Departamento de Computaci\'on\\
  Facultad de Ciencias Exactas y Naturales\\
  Universidad de Buenos Aires\\
  Buenos Aires, Argentina\\
  E-mail: \texttt{gustavolandfried@gmail.com}\\

@@

} 
\Keywords{%
\en{Learning, skill, gaming, education, sports, \proglang{Julia}, \proglang{Python},  \proglang{R}}%
\es{Aprendizaje, habilidad, videojuego, educación, deporte, \proglang{Julia}, \proglang{Python},  \proglang{R}}%
}
\Plainkeywords{%
\en{Learning, skill, gaming, education, sports, Julia, Python, R}%
\es{Aprendizaje, habilidad, videojuego, educación, deporte, Julia, Python, R}%
}

>>>>

%% - \author{} with primary affiliation
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Gustavo Landfried$^*$ \ \ \ \ Esteban Mocskos \\ \\ \small Universidad de Buenos Aires. Facultad de Ciencias Exactas y Naturales. \\ Departamento de Computaci\'on. Buenos Aires, Argentina \\ \texttt{$^*$glandfried@dc.uba.ar}}
\Plainauthor{Gustavo Landfried, Esteban Mocskos }

%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{TrueSkill Through Time: \\ the \proglang{Julia}, \proglang{Python} and \proglang{R} packages}
\Plaintitle{TrueSkill Through Time: the Julia, Python and R packages}
\Shorttitle{TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages}

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
  Gustavo Andr\'es Landfried\\
  Departamento de Computaci\'on\\
  Facultad de Ciencias Exactas y Naturales\\
  Universidad de Buenos Aires\\
  Buenos Aires, Argentina\\
  E-mail: \texttt{glandfried@dc.uba.ar}\\

@@

} 
\Keywords{%
\en{Learning, skill, Bayesian inference, gaming, education, sports, \proglang{Julia}, \proglang{Python},  \proglang{R}}%
\es{Aprendizaje, habilidad, bayes, videojuego, educación, deporte, \proglang{Julia}, \proglang{Python},  \proglang{R}}%
}
\Plainkeywords{%
\en{Learning, skill, bayesian inference, gaming, education, sports, Julia, Python, R}%
\es{Aprendizaje, habilidad, bayes videojuego, educación, deporte, Julia, Python, R}%
}
